Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-24 lloveras_2020.tex
agregadas correcciones de Chip

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physics of the solar corona, providing in particular validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework. Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

Being the {region} where the solar atmosphere is {heated, solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observation and modeling of the solar corona are tasks of great relevance to improve our understanding of the Sun-Earth environment. To advance our knowledge of the physics of the solar corona, as well as to improve its three-dimensional (3D) models, information derived from observational data plays a key role. Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona at a global scale.

@@

{To study the global coronal 3D structure, SRT proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the {quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}. The reader may refer to the review by \citet{vasquez_2016} that describes the DEMT technique and summarizes the principal publications based on it.

A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. In previous works, DEMT has been combined with a potential field source surface (PFSS) model  (\citealt{huang_2012}, \citealt{nuevo_2013}). Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic variables along different magnetic structure of the last two solar minima, and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux at the coronal base that is required to maintain stable the coronal loop structures represented by the PFSS field lines. In this article, for first time, we combined the DEMT reconstruction with the magnetic field of a magnetohydrodynamic (MHD) model, as explained in the next paragraph.

{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented. DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be compared with those reconstructed by DEMT, and on the other hand to provide MHD coronal magnetic field model that is used to study thermodynamic variables along field lines.
}

We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining fase of SC 24. To study CR-2082 with DEMT technique, data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) were used, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM, while data taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} (SDO) mission were used to study CR-2208 {for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.

@@

Section \ref{demt} and \ref{awsom} summarizes DEMT technique and AWSoM model respectively. Section \ref{trace} explains the method used to trace the thermodynamic results along the field lines of the magnetic model. Section \ref{energia} details the energy model and the loop integrated quantities. In Section \ref{demt_res} the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM results are related to the one of DEMT. Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.

@@

{We carried out the 3D DEMT reconstruction of two target CR. We selected CR-2082, a deep minimum rotation between SCs 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24. To study CR-2082 and CR-2208, as mentioned in Section \ref{intro}, data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively. The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package. For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Fistly, the fast dynamics that typically characterizes those structures is abscent from the data. Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}

{The solution of the tomographic problem involves a very large sparse matrix. Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions. }

{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}

In a first step, the time series of EUV images is used to solve a solar SRT problem, for each EUV band independently. As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately. The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel. Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series. To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}

@@

{In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI. When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the FBEs \citep{frazin_2009,nuevo_2015}. In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

\noindent 
{being the} average relative difference between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}

@@

We perform a MHD modeling of the two target rotations studied with DEMT. For this propose we use the MHD coronal model AWSOM which addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature. The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating. AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction. The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}. This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration.% \diego{falta cita}%\citep{Van2019b}.
To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. MHD equations employed within the AWSoM model are detailed in \citet{Van2014}. Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.

Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM. The model use GONG synoptic map as input for CR-2082 and ADAPT-GONG global magnetic field map for CR-2208. ADAPT-GONG maps are unavailable for CR-2082. GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component. The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields. An improvement over these maps is provided by the ADAPT model \citep{Wor2000} which creates synchronic-synoptic maps that uses supergranulation, meridional circulation, flux-transport and differential rotation to evolve the magnetic field on the Sun for better estimates of the unobserved photospheric field \citep{Arg2010, Hen2012}. 
In AWSoM, the 2D radial photospheric field is converted to 3D magnetic field using the PFSS model which specifies the initial condition. We take the source surface to be at $2.5 \, \mrsun$ and the magnetic field is radial at this height. The radial component specifies the boundary condition.
%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR2208.
Based on \citet{Cha2011} the stochastic heating exponent is taken to be 0.21 and amplitude is 0.18 to account for energy partioning between electrons and protons. The Alfv\'{e}n wave energy boundary condition is given by the poynting flux (S$_{A}$) of the outgoing wave $(\frac{S_{A}}{B})_{\odot} = 1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and the correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.

The base of the transition region (TR) forms the inner boundary of the model (at $\approx$1.0\,\rsun). To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}. In reality, the thin transition has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients excessive numerical resources are required. As described in \citet{Lio2009,Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of $\approx$ 0.001\,\rsun. This results in pushing the corona outwards. At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Consequently, AWSoM results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
\\
The computational domain for solar corona extends from 1 to 24 R$_{\odot}$. The spherical grid is radially stretched (with a maximum resolution of $0.001 \, \mrsun$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement resolves the angular size to 1.4$^\circ$ between $1 - 1.7 \, \mrsun$ and $2.8 \, \mrsun$ outside. The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid block. Local time stepping is used to speed up the steady state convergence. AWSoM simulation results provide the 3D distribution of density and temperature in addition to the 3D magnetic structure and velocity of the solar wind.

@@

{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.

@@

At this {stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell {is obtained. This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

@@

{The high temperature of the corona requires heating mechanisms to compensate for the energy losses. While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions. In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}

@@

Radiative power depends on the amount of plasma in certain temperatures that can radiate. The model estimate it by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$. This function depends on plasma temperature and is calculated by the atomic database and the plasma emission model from CHIANTI \citep{delzanna_2015}. Then, the expression for radiative power obtained is:

\begin{equation}\label{Er}
E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T),
\end{equation}

@@

{Note that, for any given field line, all quantities in these two expresions can be computed {from DEMT model} through Equations \ref{Fc}-\ref{Er}. Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}

@@

{The magnetically open and closed regions of the AWSoM model are associated to Coronal holes (CHs) and the equatorial streamer belt, respectively. Consistently with that, the {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}

@@

{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively larger values of density and temperature in comparison to the CHs. They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of {SC 25, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious. This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.

>>>>

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in particular, validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} images gathered by space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework. Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment. To advance our knowledge of the physics of the solar corona, as well as to improve and validate three-dimensional (3D) models, information derived from observational data plays a key role. Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar corona on a global scale.

@@

{To study the global coronal 3D structure, SRT has proven to be a powerful tool. Solar rotations allows instruments to compile a time series of images that cover the entire corona collecting data from many lines of sight.} In particular, differential emission measure tomography (DEMT), based on time-series of extreme ultraviolet (EUV) images, allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the {quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}. The reader may refer to the review by \citet{vasquez_2016} that describes the DEMT technique and summarizes the principal publications based on it.
\diego{chip propuso eliminar la cita de frazin 2009, no se si se confundio, xq la cita de abajo es muy similar.}

A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. In previous works, DEMT has been combined with a potential field source surface (PFSS) model  (\citealt{huang_2012}, \citealt{nuevo_2013}). Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamics of different magnetic structures along field lines found in the last two solar cycles. \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux at the coronal base that is required to maintain stable the coronal loop structures represented by the PFSS field lines. In this article, for first time, we combined the DEMT reconstruction with the magnetic field of a magnetohydrodynamic (MHD) model, as explained in the next paragraph.

{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to 1 AU (and beyond) \citep{vander_2010, Van2014}. Is constantly being validated with observations as new improvements are implemented. DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
here, we use AWSoM results with two purposes: On the one hand to provide thermodynamic results to be compared with those reconstructed by DEMT, and on the other hand to provide a MHD coronal magnetic field model that is used to study thermodynamic variables along field lines.
}

We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining phase of SC 24. To study CR-2082 with the DEMT technique, data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) are used, and Global Oscillation Network Group (GONG) magnetogram are used as the only input for AWSoM. For CR-2208 data for DEMT are taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} (SDO) mission while Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms are used for AWSoM.

@@

Section \ref{demt} and \ref{awsom} summarizes DEMT technique and AWSoM model respectively. Section \ref{trace} explains the method used to trace the thermodynamic results along the field lines of the magnetic model. Section \ref{energia} details the energy model and the loop integrated quantities. In Section \ref{demt_res}, the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM and DEMT results are compared. Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.

@@

{We carry out the 3D DEMT reconstruction of two target CRs. We select CR-2082, a deep minimum rotation between SCs 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24. To study CR-2082 and CR-2208, as mentioned in Section \ref{intro}, data taken by the STEREO/EUVI-B and SDO/AIA instruments are used, respectively. The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package. For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we \diego{opt} to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Fistly, the fast dynamics that typically characterizes those structures is abscent from the data. Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, coronal dynamics \diego{induce} artifacts are reduced compared to previous DEMT reconstructions.}

{The solution of the tomographic problem involves \diego{inversion of} a very large sparse matrix. Such inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions. }

\diego{We summarize next the main aspects of DEMT required for the analysis of this work.} In a first step, the time series of EUV images is used to solve a solar SRT problem, for each EUV band independently. As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately. The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel. Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series. To find the FBE, the tomographic problem is posed as a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}

@@

{In this work the cadence of the data time-series was set to 6\,hr and} data from three EUV bands were {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI. When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the FBEs \citep{frazin_2009,nuevo_2015}. In each tomographic voxel, the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

\noindent 
{being the} average relative difference between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} \diego{For a full description of the technique we refer the reader to \citet{frazin_2009}.}

@@

We perform MHD modeling of the two target rotations studied with DEMT. For this propose we use the MHD coronal model AWSOM which addresses coronal heating by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature. The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating. AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction. The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}. This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration.% \diego{falta cita}%\citep{Van2019b}.
To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. MHD equations employed within the AWSoM model are detailed in \citet{Van2014}. Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.

Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM. The model use GONG synoptic map as input for CR-2082 and ADAPT-GONG global magnetic field map for CR-2208. ADAPT-GONG maps are unavailable for CR-2082. GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component. The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields. An improvement over these maps is provided by the ADAPT model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation to evolve the magnetic field. These maps provide a physics based description of the unobserved polar fields \citep{Arg2010, Hen2012}. 
In AWSoM, the 2D radial photospheric field is used as a boundary condition for the 3D PFSS model which, in turn is used to specify the initial condition. We take the source surface to be at $2.5 \, \mrsun$ and the magnetic field is radial at this height. The radial component specifies the boundary condition.
%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR2208.
Based on \citet{Cha2011} the stochastic heating exponent is taken to be 0.21 and amplitude is 0.18 to account for energy partioning between electrons and protons. The Alfv\'{e}n wave energy boundary condition is given by the poynting flux (S$_{A}$) of the outgoing wave $(\frac{S_{A}}{B})_{\odot} = 1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and the correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.

The base of the transition region (TR) forms the inner boundary of the model (at $\approx$1.0\,\rsun). To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}. In reality, the thin transition has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients excessive numerical resources are required. As described in \citet{Lio2009} and \citet{Sok2013}, we artificially broaden the transition region to resolve with our finest grid resolution of $\le$ 0.001\,\rsun. This broadening pushes the corona outwards. At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Consequently, AWSoM results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
\\
The computational domain for solar corona extends from 1 to 24 R$_{\odot}$. The spherical grid is radially stretched (with a maximum resolution of $0.001 \, \mrsun$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement resolves the angular size to 1.4$^\circ$ between $1 - 1.7 \, \mrsun$ and $2.8 \, \mrsun$ outside. The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid block. Local time stepping is used to speed up the steady state convergence. AWSoM simulation results provide the 3D distribution of density and temperature in addition to the 3D magnetic structure and velocity of the solar wind.

@@

{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points. \diego{tecnicamente 97,200 = 90*180*6 como indica Chip, pero hay lineas que no son ni 0 ni 1 ni 2 y esas son las aprox 1200 que faltan!. yo pondria 97200 y evitaria aclarar.}

@@

At this {stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). 
%To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it.
 As a result, for each field line one data point per tomographic cell {is obtained. This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

@@

{The high temperature of the corona requires heating mechanisms to compensate for the energy losses. While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions. In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain stability. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}

@@

Radiative power depends on the amount of plasma in certain temperatures that can radiate.

\diego{The electrons collide with ionized metals, completely dominating the EUV radiation. Therefore the radiative power depends on the electronic density.} The flux tube model estimates by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$. This function depends on plasma temperature and is calculated by the atomic database and the plasma emission model from CHIANTI \citep{delzanna_2015}. Then, the expression for radiative power obtained is:

\begin{equation}\label{Er}
E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T).
\end{equation}

@@

\diego{where $B_0$ and $B_L$ are the values of the magnetic field at the footpoints of the loop in the coronal base.} {Note that, for any given field line, all quantities in these two expresions can be computed {from DEMT model} through Equations \ref{Fc}-\ref{Er}. Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}

@@

{The magnetically open and closed regions of the AWSoM model are associated with Coronal holes (CHs) and the equatorial streamer belt, respectively. The {location of the} open/closed boundaries derived from the respective AWSoM model quite accurately matchs {the regions of the DEMT maps, which exhibit the strongest latitudinal gradient of both the electron density and temperature.}}

@@

{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs. They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of {SC 25, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious. This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.
